---
title: ???? 
subtitle: "DANL 200: Introduction to Data Analytics"
author: 
  - name: Lily Whiting
  - name: Logan Hartstein
  - name: Tyler Thibert
date: last-modified

execute: 
  echo: true    # true false
  eval: true    # true false
  warning: false    # true false
  message: false    # true false
  fig-width: 9
  # fig-height: 5
  
format: 
  html:
    toc: true    # true false
    number-sections: true    # true false
    code-fold: show    # true false show       # https://quarto.org/docs/output-formats/html-code.html
    code-tools: true    # true false
    highlight-style: atom-one        # atom-one tango espresso   # https://quarto.org/docs/output-formats/html-code.html#highlighting
---

# Downlowds
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
beer_markets <- read_csv("https://bcdanl.github.io/data/beer_markets_all.csv")
```

# Markdown Syntax

Plain text

*DANL* and DANL

**DANL** and DANL


## Lily Graph

<br><br>


# point: child to number of beers 
```{r}
beer_markets <- beer_markets |> 
  mutate(children = 
           case_when(childrenUnder6 == T & children6to17 == T ~ 'kids under 6 to 17',
                     childrenUnder6 == T & children6to17 == F ~ 'Only 6 and under',
                     childrenUnder6 == F & children6to17 == T ~ 'Only 6 to 17',
                     childrenUnder6 == F & children6to17 == F ~ 'No kids'
           ),
         .before = childrenUnder6) |> 
  mutate(children = factor(children,
                           levels = c('No kids', 'Only 6 and under', 'Only 6 to 17','kids under 6 to 17')))

ggplot(data = beer_markets) +
  geom_histogram(mapping = aes( x = quantity,
                                fill = children),
                 position = "dodge",
                 bins = 2)
  #facet_wrap(~promo)

  # fingure out to facet wrap for promo
```

<br><br>

# Bar: How many single house hold buy beer and how  different house hold are impacted with promos
Facet 
Cow
Employment 
Education
```{r}
ggplot(data = beer_markets) +
  geom_bar(mapping = aes(x = singlefamilyhome,
                         fill = promo))

ggplot(data = beer_markets) +
  geom_histogram(mapping = aes( x = quantity,
                                fill = singlefamilyhome),
                 position = "dodge",
                 bins = 2)



```


<br><br>


# Bar: At differnt employment status How many beer do they duy and how  different employment status are impacted with promos
```{r}
ggplot(data = beer_markets) +
  geom_histogram(mapping = aes( x = quantity,
                                fill = employment),
                 position = "dodge",
                 bins = 2)
ggplot(data = beer_markets) +
  geom_bar(mapping = aes(x = employment,
                         fill = promo ))
```
<br><br>

# Bar:  differnt ages to how  many beer they buy and how  different ages are impacted with promos

```{r}
ggplot(data = beer_markets) +
  geom_histogram(mapping = aes( x = quantity,
                                fill = age),
                 position = "dodge",
                 bins = 2)
ggplot(data = beer_markets) +
  geom_bar(mapping = aes(x = age,
                         fill = promo ))
```










## Functions


<br><br>

## Packages

```{r}
library(tidyverse)
library(skimr)
```

<br><br>


# References

- [https://quarto.org/docs/output-formats/html-basics.html](https://quarto.org/docs/output-formats/html-basics.html)

- [https://quarto.org/docs/websites/](https://quarto.org/docs/websites/)

- [R for Data Science](http://r4ds.hadley.nz) by [Hadley Wickham](https://hadley.nz)

